Algebraic filtering of surfaces from medical images with Julia

### 2019-11-10 src/background.tex
paper joined and partially revised

A \emph{representation scheme} for solid modeling is a mapping between a space of mathematical models and a space of symbolic representations, often generated by a formal grammar.
Solid pointsets (i.e., `$r$-sets') are defined~\cite{Requicha:1980:RRS:356827.356833} as compact (bounded and closed) regular and semianalytic subsets of the $d$-space. A large number of representation schemes were defined in the past forty years, including the two main classes of (a) \emph{boundary representations} (`$B$-reps'), where the solid model is represented through a representation of its boundary elements, i.e.~faces, edges and vertices, and (b) \emph{decompositive/enumerative representations}, that are a decomposition of either the object or the embedding space, respectively, into a well-defined \emph{cellular complex}. In particular, a boundary representation provides a cellular decomposition of the object's boundary into \emph{cells} of dimension zero (vertices), one (edges), and two (faces). Medical imaging can be classified as \emph{enumerative representation} of cellular decompositions of organs and tissues of interest, in particular, as subsets \emph{of 3D volume elements} (voxels) from the 3D image.

@@

The \emph{Linear Algebraic Representation} (\textsc{lar})~\cite{Dicarlo:2014:TNL:2543138.2543294} aims to represent the \emph{chain complex}~\cite{TSAS} generated by a piecewise-linear geometric complex embedded either in 2D or in 3D. In few words, it gets a minimal characterization of geometry and topology of a cellular complex, i.e.~the embedding mapping $\mu : C_0 \to \E^d$ of 0-cells (vertices), as well a description of $(d-1)$-cells as subsets of vertices, and is able to return the whole chain complex 
\[ 
C_\bullet = (C_p, \partial_p) := 
C_3 \ 
\substack{
\delta_2 \\
\longleftarrow \\[-1mm]
\longrightarrow \\
\partial_3 
}
\ C_2 \ 
\substack{
\delta_1 \\
\longleftarrow \\[-1mm]
\longrightarrow \\
\partial_2 
}
\ C_1 \ 
\substack{
\delta_0 \\
\longleftarrow \\[-1mm]
\longrightarrow \\
\partial_1 
}
\ C_0 .
\] 
and, in particular, any basis for linear chain spaces $C_p$, and any linear
boundary/coboundary map \(\partial_p\) and
\(\delta_p=\partial_{p+1}^\top\) between them. The \emph{domain} of \textsc{lar} is the set of \textbf{chain complexes} generated by cell $d$-complexes ($2\leq d\leq 3$). The computer \emph{representations} of \textsc{lar} are \textbf{sparse binary matrices} to represent both the operators and the chain bases. Note that in algebraic topology a $p$-chain is defined as a linear combination of $p$-cells with scalars from a field. When the scalar coefficients are from $\{-1, 0, +1\}$, a chain may represent \emph{any (oriented) subset of cells} from the cellular complex.

We may therefore get the $(p-1)$-boundary $\partial_p \gamma_p$ of \emph{any} $p$-chain $\gamma_p$, by multiplication of the coordinate representation $[\partial_p]$ of the boundary operator times the coordinate representation $[\gamma_p]$ of the chain in terms of such scalars, i.e.~by a  matrix-vector product $ [\partial_p] [\gamma_p] $.

It is easy to understand that the \textsc{lar} representation scheme is very expressive, i.e.~that it  has a large domain,  including collections of: line segments, quads, triangles, polygons, meshes;  pixels, voxels, volume images; B-reps, enumerative and decompositive representations of solids. 
In this paper we apply \textsc{lar} methods to computation of boundary representations of solid models from segmentation (labeling) of 3D medical images.

\subsubsection{Construction of $\partial_d$ boundary matrix}

Once fixed an ordering for all the cells (vertices, edges, pixels, and voxels), i.e.~for 0-, 1-, 2-, and 3-elements of a cell partitioning of a 3D image, i.e., once fixed the $p$-bases for linear spaces $C_p$ of $p$-chains $(0\leq p\leq d)$, we call $M_p = (m_{i,j})$ the \emph{characteristic matrix} of the $p$-basis, expressed as subsets of 0-cells, where  we have that $m_{i,j}=1$ iff the $j$-th $0$-cell belongs to the $i$-th $p$-cell, and $m_{i,j}=0$ otherwise.

Note that, by computing the (sparse) matrix product $(M_{p-1} M_{p}^t) = (n_{i,j})$, with $n_{i,j} = \sum_{k} m_{i,k}m_{k,j}$, we get for each $n_{ij}$ the \emph{number of vertices} shared by $c_{p-1}^i$ and $c_{p}^j$. When this number equates the cardinality of $c_{p-1}^i$, this elementary chain is contained on the boundary of $c_{p}^j$. In a 3D image, with cubic 3-cells and squared 2-cells, everywhere we get $n_{i,j}=4$, we may state $c_{2}^i\subset\partial c_{3}^j$. In this case, by looking in each $j$ column of $M_{2} M_{3}^t = (n_{i,j})$, we have exactly \emph{six rows} where  $n_{i,j} = 4$.

Finally, consider the linear graded boundary operator $\partial_p : C_p \to C_{p-1}$. As such, it contains by columns the representation of domain basis elements, expressed as linear combination of the basis elements of the range space. Therefore, the operator matrix $[\partial_d]$ is readily obtained by setting $[\partial_d](i,j)=1$ iff $n_{i,j}=4$ and $[\partial_d](i,j)=0$ otherwise.  Of course, it will contain six non-zero elements for column.  It may be worth to remember that every 3-cell (voxel) has exactly six 2-faces.

It is possible to show that all the interesting relation of incidence/adjacency between cells of different dimensions can be both computed and efficiently queried by pairwise computing some products, with one of terms possibly transposed, of the two boundary and coboundary operator matrices $[\partial_p]$ and $[\delta_p] = [\partial_p^\top] = [\partial_p]^t$. We may also show that such matrices are \emph{very sparse}, with their sparseness growing rapidly with the dimensions (see Section~\ref{sec:block}). The pattern of non-zeros in matrix $[\partial_3]$ corresponding to a brick of shape $(4,4,4)$ is given in Figure~\ref{fig:boundary_matrix_4x4x4}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=0.75\linewidth]{figs/boundary_matrix_4x4x4.pdf} 
   \caption{A binary image of the coboundary operator  $\delta_2 = \partial^\top : C_2 \to C_3$, built for small 3D images with shape $(4,4,4)$. Note that the number of rows equates the cardinality $4\times 4\times 4 = 64$ of the voxel set; the number of columns is $d\,n\,(1+n)^{d-1} = 3\times 4\times 25 = 300$. Of course, the number of non-zeros per row (cardinality of single voxel facets) is six.}
   \label{fig:boundary_matrix_4x4x4}
\end{figure}

>>>>

A \emph{representation scheme} for solid modeling is a mapping between a space of mathematical models and a space of symbolic representations, like generated by a formal grammar.
Solid pointsets (i.e., `$r$-sets') are defined~\cite{Requicha:1980:RRS:356827.356833} as compact (bounded and closed) regular and semianalytic subsets of the $d$-space. A large number of representation schemes were defined in the past forty years, including the two main classes of (a) \emph{boundary representations} (`$B$-reps'), where the solid model is represented through a representation of its boundary elements, i.e.~faces, edges and vertices, and (b) \emph{decompositive/enumerative representations}, that are a decomposition of either the object or the embedding space, respectively, into a well-defined \emph{cellular complex}. In particular, a boundary representation provides a cellular decomposition of the object's boundary into \emph{cells} of dimension zero (vertices), one (edges), and two (faces). Medical imaging can be classified as \emph{enumerative representation} of cellular decompositions of organs and tissues of interest, in particular, as subsets \emph{of 3D volume elements} (voxels) from the 3D image.

@@

The \emph{Linear Algebraic Representation} (\textsc{lar})~\cite{Dicarlo:2014:TNL:2543138.2543294} aims to represent the \emph{chain complex}~\cite{TSAS} generated by a piecewise-linear \emph{geometric complex} embedded either in 2D or in 3D. In few words, it gets a minimal characterization of geometry and topology of a cellular complex, i.e.~the embedding mapping $\mu : C_0 \to \E^d$ of 0-cells (vertices), as well a description of $(d-1)$-cells as subsets of vertices, and is able to return the whole chain complex 
\[ 
C_\bullet = (C_p, \partial_p) := 
C_3 \ 
\substack{
\delta_2 \\x
\longleftarrow \\[-1mm]
\longrightarrow \\
\partial_3 
}
\ C_2 \ 
\substack{
\delta_1 \\
\longleftarrow \\[-1mm]
\longrightarrow \\
\partial_2 
}
\ C_1 \ 
\substack{
\delta_0 \\
\longleftarrow \\[-1mm]
\longrightarrow \\
\partial_1 
}
\ C_0 .
\] 
and, in particular, any basis for linear chain spaces $C_p$, and any linear
boundary/coboundary map \(\partial_p\) and
\(\delta_p=\partial_{p-1}^\top\) between them. The \emph{domain} of \textsc{lar} is the set of \textbf{chain complexes} generated by cell $d$-complexes ($2\leq d\leq 3$). The computer \emph{representations} of \textsc{lar} are \textbf{sparse binary matrices} to represent both the operators and the chain bases. Note that in algebraic topology a $p$-chain is defined as a linear combination of $p$-cells with scalars from a field. When the scalar coefficients are from $\{-1, 0, +1\}$, a chain may represent \emph{any (oriented) subset of cells} from the cellular complex.

We may therefore get the $(p-1)$-boundary $\partial_p c_p$ of \emph{any} $p$-chain $c_p$, by multiplication of the coordinate representation $[\partial_p]$ of the boundary operator times the coordinate representation $[c_p]$ of the chain in terms of such scalars, i.e.~by a  matrix-vector product $ [\partial_p] [c_p] $.

It is possible to show that the \textsc{lar} representation scheme is very expressive, i.e.~that it  has a large domain,  including collections of: line segments, quads, triangles, polygons, meshes;  pixels, voxels, volume images; B-reps, enumerative and decompositive representations of solids. 
In this paper we apply \textsc{lar} methods to computation of boundary representations of solid models from segmentation (labeling) of 3D medical images.
To display a triangulation of  boundary faces  in their proper position in space, the information required is contained in the \emph{geometric chain complex} (GCC):
\[
\mu: C_0\to\E^3,\ (\delta_0, \delta_1, \delta_2)
\qquad\equiv\qquad
\texttt{(geometry, topology) = (W, (EV, FE, CF))}
\]
The GCC allows to transform the (possibly non connected) boundary 2-cycle of surfaces as a standard B-rep~\cite{shapiroSM:202}. 
The \texttt{geometry} is given by
the embedding matrix \texttt{W} of vertices (0-cells), and \texttt{topology} is
given by the three sparse matrices \texttt{CF}, \texttt{FE}, \texttt{EV} of coboundaries
{i.e.},~$\delta_3, \delta_2, \delta_1$, of  chain complex describing a   
space arrangement~\cite{paoluzzi2019finite}.
Note that ordered pairs of letters from \texttt{V,E,F,C}, correspond to \emph{\emph{\texttt{V}}ertices$\to$\emph{\texttt{E}}dges$\to$\emph{\texttt{F}}aces$\to$\emph{\texttt{C}}ells} into the 
\emph{\emph{\texttt{C}}olumn$\to$\emph{\texttt{R}}ow} order of matrix maps of operators.

\subsubsection{Construction of boundary matrix $\partial_d$}

Once fixed an ordering for all the cells (vertices, edges, pixels, and voxels), i.e.~for 0-, 1-, 2-, and 3-elements of a cell partition \texttt{V,E,F,C} of a 3D image, i.e., once fixed the $p$-bases for linear spaces $C_p$ of $p$-chains $(0\leq p\leq 3)$, we call $M_p = (m_{i,j})$ the \emph{characteristic matrix} of the $p$-basis, expressed as subsets of 0-cells, where  we have that $m_{i,j}=1$ iff the $j$-th $0$-cell belongs to the boundary of $i$-th $p$-cell, and $m_{i,j}=0$ otherwise.

Note that, by computing the (sparse) matrix product $(M_{p-1} M_{p}^t) = (n_{i,j})$, with $n_{i,j} = \sum_{k} m_{i,k}m_{k,j}$, we get for each $n_{ij}$ the \emph{number of vertices} shared by $c_{p-1}^i$ and $c_{p}^j$. When this number equates the cardinality of $c_{p-1}^i$, this elementary chain is contained on the boundary of $c_{p}^j$. In a 3D image, with cubic 3-cells and squared 2-cells in between, everywhere we get $n_{i,j}=4$, we may state $c_{2}^i\subset\partial c_{3}^j$. In this case, by looking in each $j$ column of $M_{2} M_{3}^t = (n_{i,j})$, we have exactly \emph{six rows} where  $n_{i,j} = 4$.

Finally, consider the linear graded boundary operator $\partial_p : C_p \to C_{p-1}$. As such, it contains by columns the representation of domain basis elements, expressed as linear combination of the basis elements of the range space. Therefore, the operator matrix $[\partial_d]$ is readily obtained by setting $[\partial_d](i,j)=1$ iff $n_{i,j}=4$ and $[\partial_d](i,j)=0$ otherwise.  Of course, it will contain six non-zero elements for column.  It may be worth to remember that every 3-cell (voxel) of 3D image has exactly six 2-faces.

It is possible to show that all the interesting relations of incidence/adjacency between cells of different dimensions can be both computed and efficiently queried by pairwise computing some matrix products, with one of terms possibly transposed, using only the two boundary and coboundary operator matrices $[\partial_p]$ and $[\delta_p]$, and where $[\delta_p] = [\partial_p^\top]$. We~may also show that such matrices are \emph{very sparse}, with their sparseness growing rapidly with the dimensions (see Section~\ref{sec:block}). The pattern of non-zeros in matrix $[\partial_3]$ corresponding to a brick of shape $(4,4,4)$ is given in Figure~\ref{fig:boundary_matrix_4x4x4}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=0.75\linewidth]{figs/boundary_matrix_4x4x4.pdf} 
   \caption{A binary image of the coboundary operator  $\delta_2 = \partial_3^\top : C_2 \to C_3$, built for a small 3D image with shape $(4,4,4)$. Note that the number of rows equates the cardinality $4\times 4\times 4 = 64$ of the voxel set; the number of columns is $d\,n\,(1+n)^{d-1} = 3\times 4\times 25 = 300$. Of course, the number of non-zeros per row (cardinality of single voxel facets) is six, whereas the number of non-zeros per column is two, but on boundary facets.}
   \label{fig:boundary_matrix_4x4x4}
\end{figure}

### 2019-11-10 src/design.tex
paper joined and partially revised

We assume that medical devices produce 3D images with lateral dimensions that are integer multiples of some powers of two, like 128, 256, 512, etc.
Any cuboidal portion of image is completely determined by the Cartesian indices of its voxel of lowest and highest indices, and extracted by multidimensional array \emph{slicing} as $Image([\ell_x$:$h_x, \ell_y$:$h_y, \ell_z$:$h_z])$.

For the sake of simplicity, we assume a common size on the three image axes, and the corresponding image portion $\mathcal{B}$, called \emph{block}, as a function of its element of the  lowest  block  coordinates $i,j,k\in\N$ and of block dimension $n$:
\[
\mathcal{B}(i,j,k,n) := Image([in\mbox{:}in+n, jn\mbox{:}jn+n, kn\mbox{:}kn+n]) 
\]

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=0.5\linewidth]{figs/blocks} 
   \caption{A possible block partitioning of a radiologic image. The evidenced 2D block, of size $n^d=64^2$, is sliced as $\mathcal{B}([2,1,64]) = Image([128:172],[64:128)]$}
   \label{fig:blocks}
\end{figure}

Figure~\ref{fig:blocks} shows the block decomposition in a 2D image, with positive integer $u,v$ lateral sizes of image. Note that block sides do not necessarily correspond to image edges.

@@

\paragraph{Chain coordinates }\label{sec:bbbb} 
We are going to treat each image block independently from each other. Hence we map each image subspace $\mathcal{B}(i,j,n)$ to the linear \emph{chain} space $C_2$ of dimension $n\times n$, using coordinate vectors $c_{h,k}\in \\mathcal{B}^{n\times n} := \{0,1\}^{n\times n}$, where the basis element $c = c_{h,k} \in C_2$ is mapped via Cartesian-to-linear map to the binary vector 
\[
Image(h,k) \mapsto c_{h,k} := [0 \cdots 0\ 1\ 0 \cdots 0] \in \\mathcal{B}^{n\times n}
\]
for each $0\leq h,k \leq n$, and where the (single) unit element is in position $nk + h \leq n\times n$.

@@

Here we refer directly to the 3D case.
Let us call \emph{segment} the bulk content $S$ of interest within the input 3D image of size $(u,v,w)$. We aim to compute the segment boundary $\partial_3 S$. 
First we set the size $n$ of the block, in order to decompose the input $Image(u,v,w)$ into a fair number 
\[
M = \ceil{u/n} \times \ceil{v/n} \times \ceil{w/n} \simeq \frac{uvw}{n^3}
\] of blocks. 
Then we consider each image portion $c_{i,j,k} = S\cap \mathcal{B}(i,j,k,n)$ and compute its (binary) coordinate representation  $[c]_{i,j,k}\in C_3(n,n,n)$. This one is a sparse binary vector of length $n^3$. Then assemble the $M$ representations $c$ of segment portions into a sparse binary matrix $\T{S}$, of dimension $n^d \times M$. Finally compute a matrix $\T{\mathcal{B}}$ of boundary portions of $S$, represented by columns as chain coordinate vectors in $C_2$:
\[
\T{\mathcal{B}} = [\partial_3(n)]\, \T{S}.
\]
where the boundary matrix has dimension $d\,n\,(1+n)^{d-1} \times n^d$.
Of course, the $\T{\mathcal{B}}$ sparse matrix has the same column number $M$ of $\T{S}$, because each column contains the boundary representation of the corresponding $S\cap Box_{i,j,k}{i,j,k}$, and the number of rows of the operator, equal to the dimension of the linear space $C_2$.

\paragraph{Embedding}
A final computational step is needed, in order to embed the 2-chains in Euclidean space $\E^3$ and to assemble the whole resulting surface. In particular, we need to compute the \emph{embedding function} $\mu : C_0 \to \E^3$, where $C_0$ is the space of 0-chains, one-to-one corresponding to the vertices of the extracted surface. The simplest solution is to associate  four 0-cells to each 2-cell of the extracted surface, i.e.~to each non-zero entry in every column of $\T{\mathcal{B}}$.  The $\mu$ function  can be computed by identifying, via  element position in the column, a triple of integer values $0\leq x\leq u$, $0\leq y\leq v$, and $0\leq z\leq w$ for each vertex of the 2-cell.  The mapping can be implemented using a dictionary, that will store the inverse coordinate transformation used at the beginning, i.e.~the one from linear to Cartesian coords, in order of not duplicating the output vertices.

@@

All boundary surface subsets $\mathcal{B}_{i,j,k}(S) = \partial_3 S \cap \mbox{Box}_{i,j,k}$, provided by  columns of $\T{S}$, are embedded in the same coordinate space. In formal terms: 
\[
\texttt{Lar}(S) := (\texttt{Geom}(S), \texttt{Top}(S)) = (\texttt{V}, \texttt{CV}),
\]
where, with respect to the \emph{chain complex} $C_3\to C_2\to C_1\to C_0$ induced by the input image $Im$ and segment $S_{i,j,k}$, we get
\begin{align}
\texttt{Geom} &:= \mu(C_0(_{i,j,k})) = \texttt{V},
\\
\texttt{Top} &:= C_3(S) = \T{S} \mapsto \texttt{CV}.
\end{align}
and
\begin{align}
\texttt{Lar}(B_{i,j,k}) &:= (\texttt{Geom}, \texttt{Top}) = (\texttt{W}, \texttt{FW}),
\\
\texttt{Geom} &:= \mu(C_0(B_{i,j,k})) = \texttt{W} \subset \texttt{V},
\\
\texttt{Top} &:= C_2(B_{i,j,k}) = \T{\mathcal{B}}_{i,j,k} \mapsto \texttt{FW} \subset \texttt{FV}.
\end{align}

A translation transformation applied to each vertex subset $\texttt{W}_{i,j,k}$ with translation  vector $\v{t} = [i,j,k]$ will therefore move it in the final space position, so finally giving
\[
\texttt{Lar}(\mathcal{B}) = \oplus_{i,j,k}\texttt{Lar}(\partial_3 S_{i,j,k})) = \oplus_{i,j,k}(\texttt{W}, \texttt{FW}) .
\]

>>>>

We assume that medical devices produce 3D images with lateral dimensions that are integer multiples of some powers of two, like 128, 256, 512, etc.
Any cuboidal portion of image is completely determined by the Cartesian indices of its voxels of lowest and highest indices, and extracted by multidimensional array \emph{slicing} as $Image([\ell_x$:$h_x, \ell_y$:$h_y, \ell_z$:$h_z])$.

For the sake of simplicity, we assume a common size on the three image axes, and the corresponding image portion $\B$, called \emph{block}, as a function of its element of the  lowest  block  coordinates $i,j,k\in [1:n]$ and of block dimension $n\in\N$:
\[
\B(i,j,k,n) := Image([in:in+n, jn:jn+n, kn:kn+n]) 
\]

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=0.5\linewidth]{figs/blocks} 
   \caption{A possible block partitioning of a radiologic image. The evidenced 2D block, of size $n^d=64^2$, is sliced by $\B([2,1,64]) = Image([128:172],[64:128)]$}
   \label{fig:blocks}
\end{figure}

Figure~\ref{fig:blocks} shows the block decomposition in a 2D image, with positive integers $(u,v)$ giving the lateral sizes of image. Note that block sides do not necessarily correspond to image edges.

@@

\paragraph{Chain coordinates }\label{sec:bbbb} 
We are going to treat each image block independently from each other. Hence we map each image subspace $\B(i,j,n)$ to the linear \emph{chain} space $C_2$ of dimension $n\times n$, using coordinate vectors $c_{h,k}\in \\B^{n\times n} := \{0,1\}^{n\times n}$, where the basis element $c = c_{h,k} \in C_2$ is mapped via Cartesian-to-linear map to the binary vector 
\[
Image(h,k) \mapsto c_{h,k} := [0 \cdots 0\ 1\ 0 \cdots 0] \in \B^{n\times n}
\]
for each $0\leq h,k \leq n$, and where the (single) unit element is in position $nk + h \leq n\times n$.

@@

Here we refer directly to the 3D case.
Let us call \emph{segment} the bulk content $S$ of interest within the input 3D image of size $(u,v,w)$. We aim to compute the segment boundary $\partial_3 S$. 
First we set the size $n$ of the block, in order to decompose the input $Image(u,v,w)$ into a fair number 
\[
M = \ceil{u/n} \times \ceil{v/n} \times \ceil{w/n} \simeq \frac{uvw}{n^3}
\] of blocks. 
Then we consider each image portion $c_{i,j,k} = S\cap \B(i,j,k,n)$ and compute its (binary) coordinate representation  $[c]_{i,j,k}\in C_3(n,n,n)$. This one is a sparse binary vector of length $n^3$. Then assemble the $M$ representations $c$ of segment portions into a sparse binary matrix $\T{S}$, of dimension $n^d \times M$. Finally compute a matrix $\T{\B}$ of boundary portions of $S$, represented by columns as chain coordinate vectors in $C_2$:
\[
\T{\B} = [\partial_3(n)]\, \T{S}.
\]
where the boundary matrix has dimension $d\,n\,(1+n)^{d-1} \times n^d$.
Of course, the $\T{\B}$ sparse matrix has the same column number $M$ of $\T{S}$, because each column contains the boundary representation of the corresponding $S\cap Box_{i,j,k}{i,j,k}$, and the number of rows of the operator, equal to the dimension of the linear space $C_2$.

\paragraph{Embedding}
A final computational step is needed, in order to embed the 2-chains in Euclidean space $\E^3$ and to assemble the whole resulting surface. In particular, we need to compute the \emph{embedding function} $\mu : C_0 \to \E^3$, where $C_0$ is the space of 0-chains, one-to-one corresponding to the vertices of the extracted surface. The simplest solution is to associate  four 0-cells to each 2-cell of the extracted surface, i.e.~to each non-zero entry in every column of $\T{\B}$.  The $\mu$ function  can be computed by identifying, via  element position in the column, a triple of integer values $0\leq x\leq u$, $0\leq y\leq v$, and $0\leq z\leq w$ for each vertex of the 2-cell.  The mapping can be implemented using a dictionary, that will store the inverse coordinate transformation used at the beginning, i.e.~the one from linear to Cartesian coords, in order of not duplicating the output vertices.

@@

All boundary surface subsets $\B_{i,j,k}(S) = \partial_3 S \cap \mbox{Box}_{i,j,k}$, provided by  columns of $\T{S}$, are embedded in the same coordinate space. In formal terms: 
\[
\texttt{Lar}(S) := (\texttt{Geom}(S), \texttt{Top}(S)) = (\texttt{V}, \texttt{CV}),
\]
where, with respect to the \emph{chain complex} $C_3\to C_2\to C_1\to C_0$ induced by the input image $Im$ and segment $S_{i,j,k}$, we get
\begin{align}
\texttt{Geom} &:= \mu(C_0(_{i,j,k})) = \texttt{V},
\\
\texttt{Top} &:= C_3(S) = \T{S} \mapsto \texttt{CV}.
\end{align}
and
\begin{align}
\texttt{Lar}(B_{i,j,k}) &:= (\texttt{Geom}, \texttt{Top}) = (\texttt{W}, \texttt{FW}),
\\
\texttt{Geom} &:= \mu(C_0(B_{i,j,k})) = \texttt{W} \subset \texttt{V},
\\
\texttt{Top} &:= C_2(B_{i,j,k}) = \T{\B}_{i,j,k} \mapsto \texttt{FW} \subset \texttt{FV}.
\end{align}

A translation transformation applied to each vertex subset $\texttt{W}_{i,j,k}$ with translation  vector $\v{t} = [i,j,k]$ will therefore move it in the final space position, so finally giving
\[
\texttt{Lar}(\B) = \oplus_{i,j,k}\texttt{Lar}(\partial_3 S_{i,j,k})) = \oplus_{i,j,k}(\texttt{W}, \texttt{FW}) .
\]
